Local Spectral Clustering of Density Upper Level Sets

### 2019-05-07 arxiv/arxiv_local_density_clustering_proofs.tex
aPPR and misclassification rates added, proofs refined

\let\pprspace\relax
\externaldocument{arxiv_local_density_clustering}

@@

%%% Graph terms
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\degminpr}{\deg_{\min}'}
\newcommand{\piminwt}{\widetilde{\pibf}_{\min}}

@@

We will employ a sharper concentration inequality for $\sum_{i = 1}^{n} X_i$.
\begin{lemma}
	\label{lem: multiplicative_Hoeffding}
	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \Ebb(\sum_{i = 1}^n X_i)$. Then,
	\begin{align*}
	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{3}\right) \\
	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\delta^2 \mu}{2}\right)
	\end{align*}
\end{lemma}

\begin{lemma}
	\label{lem: ball_bounds_in_probability}
	Let $\Csig$ satisfy the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}. For $r < \sigma$, the following statements hold with probability tending to one as $n \to \infty$:
	\begin{align*}
	D_{\min}(\Csig[X]; \widetilde{G}_{n,r}) & \geq \frac{1}{2} \nu_d r^d \lambda_{\sigma} \\
	D_{\max}(\Csig[X]; \widetilde{G}_{n,r}) & \leq 2 \nu_d r^d \Lambda_{\sigma} \\
	\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r}) & \leq 2 \nu(\Csig) \Lambda_{\sigma}
	\end{align*}
	where $D_{\min}(\Csig[X]; \widetilde{G}_{n,r})$ is the minimum degree of any vertex $v \in \Csig[X]$ in the subgraph $\widetilde{G}_{n,r}$, and analogously for $D_{\max}(\Csig[X]; \widetilde{G}_{n,r})$.
\end{lemma}

The statement follows immediately from Lemma \ref{lem: ball_bounds}.

@@

Recall that for teleportation parameter $\alpha  \in (0,1]$ and seed node $v \in \Xbf$, we write $\pbf(v, \alpha; G_{n,r})$ for the \pprspace vector computed over neighborhood graph $G_{n,r}$; let $\pbf(u)$ denote the entry of $\pbf(v, \alpha; G_{n,r})$ at vertex $u \in \Xbf$. 
Recalling that we write $\widetilde{\pibf}_{n,r}$ for the stationary distribution over $\widetilde{G}_{n,r}$, write $\widetilde{\pibf}_{n,r}(u)$ denote the stationary distribution at vertex $u \in \Csig[\Xbf]$.

Lemma \ref{lem: setup} states the key results needed to link Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound} with Theorem \ref{thm: consistent_recovery_of_density_clusters}.  
\begin{lemma} 
	\label{lem: setup}
	Let $0 < r < \sigma$ and
	\begin{equation} 
	\label{eqn: upper_bound_alpha}
	\frac{\Psi_{n,r}(\Csig[\Xbf])}{10} \leq \alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}.
	\end{equation}

	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following statements hold with respect to $\pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For each $u \in \Cset[\Xbf]$,
		\begin{equation}
		\label{eqn: lower_bound_PPR_in_cluster}
		\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Csig'[\Xbf]$,
		\begin{equation}
		\label{eqn: upper_bound_PPR_in_other_cluster}
		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}
		\end{equation}
		where $ \deg_{\min}' := \min_{u \in \Cset'[\Xbf]} \deg(u; G_{n,r})$. 
	\end{itemize}
\end{lemma}

\begin{proof}
	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. We begin with some notation. Recall that $\Wbf_n = \Dbf_n \Abf_n^{-1}$ is the transition probability matrix over $G_{n,r}$. Let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$. Then, given $q \in \Reals^{\Csig[\Xbf]}$ we let
	\begin{equation}
	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}_n 
	\end{equation}
	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$. (When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).

	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align}
	\label{eqn: leakage_soakage}
	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
	\end{align}
	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.

	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step. For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$. By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$. The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.

	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation. By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
	\begin{equation}
	\label{eqn: zhulemma3.1}
	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u),~ \textrm{and}~ \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
	\end{equation}
	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)

	If additionally $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
	\begin{equation*}
	\widetilde{\pbf}(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u)
	\end{equation*}
	and along with \eqref{eqn: zhulemma3.1}, we obtain
	\begin{equation*}
	\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
	\end{equation*}

	We proceed to upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \widetilde{D}_{\min}$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}. We observe two facts regarding $\widetilde{\pbf}_{\ell}(u)$. First, for any $u \in \Cset$, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well. Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
	\begin{align}
	\label{eqn: one_step_bound}
	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
	& \leq \frac{1}{\widetilde{D}_{\min}} 
	\end{align}
	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}$.

	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
	\begin{align*}
	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
	& \leq \norm{\ell}_1 \frac{1}{\widetilde{D}_{\min}}.
	\end{align*}
	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.

@@

We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.
\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
~

Observe that the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirement of Lemma \ref{lem: setup}, and therefore by that lemma we have the following bounds:
\begin{align*}
\pbf(u) & \geq \frac{4}{5} \widetilde{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}} \tag{for each $u \in \Cset[\Xbf]$} \\
\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \tag{for each $u' \in \Cset'[\Xbf]$}
\end{align*}

>>>>

\let\pprspace\relax
\let\ppr\relax
\externaldocument{arxiv_local_density_clustering}

@@

%%% Graph terms
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\degminpr}{\deg_{\min}'}
\newcommand{\degminwt}{\widetilde{\deg}_{\min}}
\newcommand{\degmaxwt}{\widetilde{\deg}_{\max}}
\newcommand{\degmax}{\deg_{\max}}
\newcommand{\piminwt}{\widetilde{\pibf}_{\min}}
\newcommand{\piminpr}{\pibf_{\min}'}
\newcommand{\degmin}{\deg_{\min}}

@@

We will employ a sharper concentration inequality for $\sum_{i = 1}^{n} X_i$.
\begin{lemma}
	\label{lem: multiplicative_Hoeffding}
	Let $X_i \in \set{0,1}$ for $i = 1, \ldots, n$ and let $\mu = \Ebb(\sum_{i = 1}^n X_i)$. Then,
	\begin{align*}
	\Pbb\left(\sum_{i=1}^{n}X_i > (1 + \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{3}\right) \\
	\Pbb\left(\sum_{i=1}^{n}X_i < (1 - \epsilon) \mu \right) \leq \exp \left(\frac{-\epsilon^2 \mu}{2}\right)
	\end{align*}
\end{lemma}

We will require asymptotic bounds on several different degree and volume functionals, which follow from Lemma \ref{lem: multiplicative_Hoeffding}. Let
\begin{alignat*}{2}
\degminwt & := \min_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]),~ && \degmaxwt := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}\left[\Csig[\Xbf]\right]) \\ 
\degminpr & := \min_{u \in \Csig'[\Xbf]} \deg(u; G_{n,r}),~ && \degmax := \max_{u \in \Csig[\Xbf]} \deg(u; G_{n,r}) \\
\degmin & := \min_{u \in \Csig{\Xbf}} \deg(u; G_{n,r}).
\end{alignat*}

\begin{lemma}
	\label{lem: ball_bounds_in_probability}
	Under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, for any $\epsilon > 0$, each of the following bounds hold with probability tending to one as $n \to \infty$:
	\begin{align}
	\frac{\degminwt}{n}, \frac{\degminpr}{n} & \geq (1 - \epsilon)\frac{6}{25} \lambda_{\sigma} r^d \nu_d \label{eqn: min_cluster_degree_bound} \\
	\frac{\degmin}{n} & \geq  (1 - \epsilon) \lambda_{\min} r^d \nu_d \label{eqn: min_degree_bound} \\
	\frac{\degmax}{n} & \leq (1 + \epsilon) \Lambda_{\sigma} r^d \nu_d \label{eqn: max_degree_bound}\\
	\frac{\abs{\Csig[\Xbf]}}{n} & \leq \Pbb(\Csig)(1 + \epsilon) \label{eqn: Csig_cardinality_bound}\\
	\label{eqn: volwt_bound}
	\frac{1}{2}\vol_0 \leq \vol_{n,r}(\Csig[\Xbf]) & \leq \frac{3}{2} \vol_0
	\end{align}
\end{lemma}
\begin{proof}
	We note that for any $x \in \Csig \cup \Csig'$, by \ref{asmp: bounded_density} and \ref{asmp: C'_bounded_density} along with Lemma \ref{lem: local_conductance},
	\begin{equation*}
	\frac{6}{25} \lambda_{\sigma} r^d \nu_d \leq \Pbb(B(x,r))
	\end{equation*}
	Then, by Lemma \ref{lem: multiplicative_Hoeffding} along with a union bound
	\begin{equation*}
	\Pbb \left(\degminwt \leq n (1 - \epsilon) \frac{6}{25}  \lambda_{\sigma} r^d \nu_d \right) \leq n \exp\set{- \frac{6 n \epsilon^2  \lambda_{\sigma} r^d \nu_d}{50} } \overset{n \to \infty}{\longrightarrow} 0.
	\end{equation*}
	As the same bound holds for $\degminpr$, \eqref{eqn: min_cluster_degree_bound} is shown. \eqref{eqn: min_degree_bound} and \eqref{eqn: max_degree_bound} follow from similar reasoning.

	\eqref{eqn: Csig_cardinality_bound} follows directly from the law of large numbers.

	Finally, note that
	\begin{equation*}
	\vol_{n,r}(\Csig[\Xbf]) = \sum_{i = 1}^{n} \sum_{j \neq i}^{n} \1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)
	\end{equation*}
	can be rewritten as a U-statistic, and furthermore
	\begin{equation*}
	\int_{\Csig} \Pbb(B(x,r)) dx = \Ebb\left(\1(x_i \in \Csig) \1(\norm{x_i - x_j} \leq r)\right).
	\end{equation*}

	Therefore by Lemma \ref{lem: bounded_difference}
	\begin{equation}
	\label{eqn: ball_bounds_in_probability_1}
	\abs{\widetilde{\vol}_{n,r}(\Csig[\Xbf]) - n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx }\leq \frac{3}{20}n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx 
	\end{equation}
	with probability at least $1 - 2\exp(-\frac{3}{20}n \int_{\Csig} \Pbb(B(x,r) dx) \to 0$ as $n \to \infty$. Then, application of the triangle inequality to \eqref{eqn: ball_bounds_in_probability_1}, along with the range $\vol_0 \in [3/4,5/4] \cdot n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx$ given by \eqref{eqn: initialization}, yields
	\begin{equation*}
	\abs{\widetilde{\vol}_{n,r}(\Csig[\Xbf]) - \vol_0} \leq \left(\frac{3}{20} + \frac{1}{4}\right) n(n-1)\int_{\Csig} \Pbb(B(x,r)) dx \leq \frac{1}{2} \vol_0.
	\end{equation*}
\end{proof}

\subsection{Proof of Theorem \ref{thm: misclassification_rate}}
\label{sec: proof_of_misclassification_rate}

In this section, we prove both Theorem \ref{thm: misclassification_rate} and the relevant portions of Corollary \ref{cor: appr}.

Lemma \ref{lem: zhu} is a restatement of Lemma 3.4 of \cite{zhu2013}, translated into notation consistent with the rest of this paper. It is stated with respect to an arbitrary $A \subseteq G = (V,E)$, and a good set $A^g \subseteq A$ with $\vol(A^g; G) \geq \vol(A; G)/2$. \footnote{The sweep cuts of Lemma 3.4 of \cite{zhu2013} are stated directly with respect to $\vol(A;G)$, rather than $\vol_0$; this discrepancy leads to the extra factors of $1 - c$ and $1 + c$ which appear in our bounds as opposed to theirs.}

\begin{lemma}
	\label{lem: zhu}
	Let $\epsilon \geq 0$, $v \in A^g$, $\alpha \leq \frac{\Psi(A; G)}{9}$, and $\vol_0 \in [1 - c,1 + c] \vol(A;G)$ for $0 < c < 1$. Consider taking sweep cuts of the \textcolor{red}{approximate \pprspace vector} $\pbf^{(\epsilon)} := \pbf^{(\epsilon)}(v,\alpha; G)$ of the form
	\begin{equation*}
	S_{\beta} := \left\{u \in V: \pbf^{(\epsilon)} \geq \beta \frac{\deg(u; G)}{\vol_0} \right\}
	\end{equation*}

	For any $\beta < \frac{3}{5(1 + c)}$, and $\epsilon \leq \frac{1}{10} \vol(A;G)$ the following bounds hold:
	\begin{align}
	\vol(S_{\beta} \setminus A; G) \leq \frac{2\Phi(A;G)}{\alpha \beta(1 - c)} \vol(A; G), \label{eqn: zhu_1}\\
	\vol(A \setminus S_{\beta}; G) \leq \left(\frac{2\Phi(A;G)}{\alpha (\frac{3}{5} - \beta(1 + c))} + 8\Phi(A;G)\right)\vol(A; G),  \label{eqn: zhu_2}
	\end{align}
\end{lemma}

\paragraph{Proof of Theorem \ref{thm: misclassification_rate}.}

Observe that by Theorem \ref{thm: inverse_mixing_time_lower_bound} and the upper bounds $\alpha \leq \frac{\mathbf{\Psi}(\theta)}{9}, r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$. Moreover, i) we restrict $v \in \Csig[\Xbf]^g$; ii) the output of Algorithm \ref{alg: ppr} $\widehat{C} = S_{\beta}$ for some $1/40 < \beta < 1/11$; iii) by Lemma \ref{lem: ball_bounds_in_probability}, $\vol_0 \in [1/2,3/2]\vol_{n,r}(\Csig[\Xbf])$, and iv) the \pprspace vector $\pbf(v,\alpha;G_{n,r})$ is simply an approximate \pprspace vector with $\epsilon = 0$. All conditions of Lemma \ref{lem: zhu} are therefore satisfied, and consequently by \eqref{eqn: zhu_1}, \eqref{eqn: zhu_2}, Theorem \ref{thm: conductance_upper_bound}, and the lower bound $\alpha \geq \mathbf{\Psi}(\theta)/10$, the following bounds hold with probability tending to 1 as $n \to \infty$:
\begin{equation*}
\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) \leq 1600 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf]), \quad \textrm{and} \quad  \vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) \leq 52 \kappa(\Cset) \vol_{n,r}(\Csig[\Xbf])
\end{equation*}
Noting that
\begin{align*}
\vol_{n,r}(\widehat{C} \setminus \Csig[\Xbf]) & \geq \abs{\widehat{C} \setminus \Csig[\Xbf]} \min_{x \in \Xbf} \{\deg_{n,r}(x)\} \\
\vol_{n,r}(\Csig[\Xbf] \setminus \widehat{C}) & \geq \abs{\Csig[\Xbf] \setminus \widehat{C}} \min_{x \in \Csig[\Xbf]} \{\deg_{n,r}(x)\},~ \textrm{and} \\
\vol_{n,r}(\Csig[\Xbf]) & \leq \abs{\Csig[\Xbf]} \max_{x \in \Csig[\Xbf]} \set{\deg_{n,r}(x)}
\end{align*}
the claim follows in light of Lemma \ref{lem: ball_bounds_in_probability}.

\paragraph{Proof of Corollary \ref{cor: appr} misclassification rates.}

The choice $\epsilon = \frac{1}{20 \vol_0}$, along with Lemma \ref{lem: ball_bounds_in_probability} and the upper bound on $\vol_0$ given by \eqref{eqn: initialization}, together imply that $\epsilon < \frac{1}{10}\vol_{n,r}(\Csig[\Xbf])$ with probability tending to one as $n \to \infty$. We may therefore apply Lemma \ref{lem: zhu} with respect to $\pbf^{(\epsilon)}$. All other aspects of the proof of Theorem \ref{thm: misclassification_rate} may be applied exactly as stated.

@@

We begin with some notation. Let $\widetilde{\Dbf}$ and $\widetilde{\Wbf}$ be the degree and random walk matrices for the induced subgraph $G_{n,r}(\Csig[\Xbf]) = \widetilde{G}_{n,r}$, with vertex set $\widetilde{V} = \Csig[\Xbf]$ and edge set $\widetilde{E} = \set{(u,v) \in G_{n,r}: u,v \in \Csig[\Xbf]}$. Consider the function $\overline{\pibf}_{n,r}: \Csig[\Xbf] \to [0,1]$ 
\begin{equation*}
\overline{\pibf}_{n,r}(x) := \frac{\widetilde{\deg}_{n,r}(x)}{\vol_{n,r}(\Csig[\Xbf])}.
\end{equation*}
(Note $\overline{\pibf}_{n,r}$ is distinct from $\widetilde{\pibf}_{n,r}$, as we normalize by $\vol_{n,r}(\Csig[\Xbf])$ rather than $\widetilde{\vol}_{n,r}(\Csig[\Xbf])$.)

Lemma \ref{lem: setup} provides uniform error bounds on $\pbf(u) - \overline{\pibf}_{n,r}(u)$ over all $x \in \Xbf$ (where in an abuse of notation we consider $\overline{\pibf}_{n,r}(x) = 0$ for $x \in \Xbf \setminus \Csig[\Xbf]$). 
\begin{lemma} 
	\label{lem: setup}
	Let $0 < r < \sigma$ and $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$. Then the following statement holds: there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following bounds hold with respect to $\pbf := \pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For each $u \in \Cset[\Xbf]$,
		\begin{equation}
		\label{eqn: lower_bound_PPR_in_cluster}
		\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{20 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminwt}
		\end{equation}
		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Cset'[\Xbf]$,
		\begin{equation}
		\label{eqn: upper_bound_PPR_in_other_cluster}
		\pbf(u') \leq \frac{20 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}.
		\end{equation}
	\end{itemize}
\end{lemma}

\begin{proof}
	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. Given starting distribution $q$ with $\mathrm{supp}(q) \subseteq \Csig[\Xbf]$, we let
	\begin{equation}
	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}
	\end{equation}
	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$. (When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \widetilde{V}$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).

	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align}
	\label{eqn: leakage_soakage}
	\ell_t & := e_v (\Wbf \widetilde{\mathbf{I}} )^t (\mathbf{I} - \Dbf^{-1} \wDbf),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
	s_t & := e_v (\Wbf \widetilde{\mathbf{I}} )^t (\Wbf \widetilde{\mathbf{I}}^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
	\end{align}
	where $\mathbf{I}$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}$ is an $n \times n$ diagonal matrix with $\widetilde{\mathbf{I}}_{xx} = 1$ if $x \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}^c = \mathbf{I} - \widetilde{\mathbf{I}}$.

	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk over $G_{n,r}$ originating from $v \in \Csig[\Xbf]$ stays within $\widetilde{G}_{n,r}$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step. For $w \in \Xbf \setminus \Csig[\Xbf]$, $\ell_t(w) = 0$. By contrast, for $w$ again in $\Xbf \setminus \Csig[\Xbf]$, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then is soaked up into $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$. The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.

	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation. By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
	\begin{equation}
	\label{eqn: zhulemma3.1}
	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u), \quad \textrm{and} \quad \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
	\end{equation}
	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)

	If additionally $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
	\begin{equation*}
	\widetilde{\pbf}(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u)
	\end{equation*}
	and along with \eqref{eqn: zhulemma3.1}, we obtain
	\begin{equation*}
	\pbf(u) \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
	\end{equation*}

	We proceed to show the upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \degminwt$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}. We note two facts regarding $\widetilde{\pbf}_{\ell}(u)$, which hold for all $u \in \Cset[\Xbf]$. First, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well. Second, for any $q$ such that $\sum_{w \in \Csig[\Xbf]} q(w) \leq 1$, and any $t \geq 1$,
	\begin{align}
	\label{eqn: one_step_bound}
	q \widetilde{\Wbf}^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
	& \leq \frac{1}{\degminwt} 
	\end{align}
	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \degminwt$.

	These facts, along with some basic algebra, lead to the desired lower bound on $\widetilde{\pbf}_{\ell}(u)$ for every $u \in \Cset[\Xbf]$:
	\begin{align*}
	\widetilde{\pbf}_{\ell}(u) & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\ell \widetilde{\Wbf}_n^t \right)(u)  \nonumber \\
	& = \norm{\ell}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
	& = \norm{\ell}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{\ell}{\norm{\ell}_1}  \widetilde{\Wbf}_n^t \right)(u)\nonumber \\
	& \leq \frac{\norm{\ell}_1 }{\degminwt}.
	\end{align*}
	and \eqref{eqn: lower_bound_PPR_in_cluster} is proved.

@@

We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.

\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
~

In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
